Boundary Labeling for annotated documents

### 2017-11-16 LaTeX/Paper.tex
Paper: Completed new Graph Terminology drawing, added to paper. Program: No changes.

\begin{figure}%{r}{0.35\textwidth}
 \captionsetup{justification=centering, margin=0.75cm}
 \centering
  \includegraphics[scale=0.5]{IPE_TerminologyDrawing.pdf}
  \caption{Illustrated guide to the labeling terminology}
 \label{fig:term}
\end{figure}

A \emph{graph} $G=\langle V, E \rangle$ is a tuple of \emph{vertices} $V=\{v_1, v_2, ..., v_n\}$ and \emph{edges} $E=\{e_1, e_2, ..., e_m\}$. A vertex $v$ is a featureless object. %Wie  sage ich, dass die Umsetzung der Vertices sehr flexibel ist?
 Each edge $e$ is a relation between two vertices $E \subseteq V\times V$. %Edges can also be directional, or have a weight, which affects how they are treated by algorithms.
We call two vertices $u,v \in V$ \emph{adjacent}, if the edge $e=(u,v) \in E$.
 A \emph{path} $P=v_1, ..., v_h$ is an ordered sequence of vertices, where each vertex must have an edge connecting it to the subesquent one.
 \emph{Depth-first search} is a searching algorithm on a graph G that starts at a given vertex $v \in V$ and explores the graph by traversing its edges as far as possible before backtracking. In our algorithm, the goal is to reach a target vertex $v_t \in V$, at which point the algorithm terminates and returns the route taken from $v_s$ to $v_t$.
% A search algorithm is \emph{monotonous} if, for each vertex $v$ and each successor $v'$ generated by the algorithm, the estimated cost of reaching the goal from $v$ is not greater than the cost of reaching $v'$ plus the estimated cost of reaching the goal from $v'$.

\emph{Polylines} are a connected series of \emph{line segments}. Line segments are straight lines that contain each point between their starting and end point. 
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{Label area} which is a rectangular area designated to hold labels. It is located next to of the bigger \emph{text area}, which contains the document's text and all \emph{sites}, the points or objects that a label's information refers to. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and einding points in a straight line.
The leader's name is created by combining the name of the segments - for example, the leader from Fig~\ref{fig:term} would be classified as an OPO-Leader.%Re-write once picture is updated
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity

>>>>

\begin{figure}%{r}{0.35\textwidth}
 \captionsetup{justification=centering, margin=0.75cm}
 \centering
  \includegraphics[scale=0.90]{GraphTerminologyExtended.png}
  \caption{Illustrated guide to the labeling terminology}
 \label{fig:term}
\end{figure}

A \emph{graph} $G=\langle V, E \rangle$ is a tuple of \emph{vertices} $V=\{v_1, v_2, ..., v_n\}$ and \emph{edges} $E=\{e_1, e_2, ..., e_m\}$. A vertex $v$ is a featureless object. %Wie  sage ich, dass die Umsetzung der Vertices sehr flexibel ist?
 Each edge $e$ is a relation between two vertices $E \subseteq V\times V$. %Edges can also be directional, or have a weight, which affects how they are treated by algorithms.
We call two vertices $u,v \in V$ \emph{adjacent}, if the edge $e=(u,v) \in E$.
 A \emph{path} $P=v_1, ..., v_h$ is an ordered sequence of vertices, where each vertex must have an edge connecting it to the subesquent one.
 \emph{Depth-first search} is a searching algorithm on a graph G that starts at a given vertex $v \in V$ and explores the graph by traversing its edges as far as possible before backtracking, and continues to do so until a pre-defined goal is met. %In our algorithm, the goal is to reach a target vertex $v_t \in V$, at which point the algorithm terminates and returns the route taken from $v_s$ to $v_t$.
% A search algorithm is \emph{monotonous} if, for each vertex $v$ and each successor $v'$ generated by the algorithm, the estimated cost of reaching the goal from $v$ is not greater than the cost of reaching $v'$ plus the estimated cost of reaching the goal from $v'$.

\emph{Polylines} are a connected series of \emph{line segments}. Line segments are straight lines that contain each point between their starting and end point. 
\emph{Labels} hold additional information and are represented as boxes containing this information. They are usually placed in the \emph{Label area} which is a rectangular area designated to hold labels. It is located next to of the bigger \emph{text area}, which contains the document's text and all \emph{sites}, the points or objects that a label's information refers to. The site and the label are connected via a \emph{leader}, a polyline that can be further classified by looking at the orientation of its segments: \emph{O-Segments} run orthogonally to the border of the label area. \emph{P-Segments} run parallel to the border of the label area, and as such must be combined with other segments for the leader to reach its destination. \emph{S-Segments} are not required to have any particular orientation, and simply connect their start and einding points in a straight line.
The leader's name is created by combining the name of the segments - for example, the blue leader from Fig~\ref{fig:term} would be classified as an OPOPO-Leader.%Re-write once picture is updated
The location where a leader connects to the label is called the \emph{port}. It can be restricted to pre-defined positions. %TODO: Re-insert monotonicity
